Draft Exploration

### 2020-04-22 draft_exploration.Rmd
commenting redraft_gap
named Rmd code chunks

@@

@@

@@

@@

@@

```{r, echo=FALSE}
draft_2000_2012 <- draft %>%
  filter(year >= 1990 & year <= 2011)

@@

```{r, echo=FALSE}
grow_talent <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(decade = ifelse(year %in% 1970:1979, 1970,
                                 ifelse(year %in% 1980:1989, 1980,
                                        ifelse(year %in% 1990:1999, 1990,
                                               ifelse(year %in% 2000:2009, 2000,
                                                      ifelse(year %in% 2010:2019, 2010, NA)))))) %>%
  filter(year >= 1980 & year <= 2009) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(teamname) %>%
  summarize(mlb = sum(mlb_made), 
            total = sum(ignore),
            percent_mlb = sum(mlb_made) / sum(ignore))

@@

@@

```{r, echo=FALSE}
college_signed <- master %>%
  filter(source == "C" & signed == "Y") %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))

@@

@@

@@

@@

@@

```{r, include=FALSE}
ggsave("final_project_shiny/redraft_probability.png")
```

```{r, echo=FALSE}
redraft_table %>%
  ggplot(aes(round, mean_round_diff)) +
  geom_point(na.rm = TRUE) +
  geom_line(aes(group = start_year, color = start_year), na.rm = TRUE) +
  labs(
    x = "Round Range Drafted out of High School",
    y = "Average Improvement Re-draft Round",
    color = "Time Frame",
    title = "Average Change in Round of Re-drafted Unsigned High School Picks",
    subtitle = "Organized by initial round range and time period"
  ) +
  theme_light() +
  scale_color_viridis_c() +
  scale_x_continuous(breaks = c(5, 10, 20, 30, 40, 50)) +
  scale_y_continuous(breaks = c(-10, -5, 0, 10, 20)) +
  geom_hline(color = "red", linetype = "dashed", yintercept = 0)
```

@@

@@

@@

@@

@@

@@

```{r, echo=FALSE}
state_mlb %>%
  filter(big_state == 0) %>%
  ggplot(aes(full, drafted, color = percent_mlb)) +
  coord_flip() +
  geom_point() +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300, 350)) +
  theme_gray() +
  theme(axis.text.y = element_text(size = 7.5)) +
  scale_color_viridis_c() +
  labs(
    x = "State",
    y = "Number of Players Drafted",
    title = "Number of High School Players Drafted by State",
    subtitle = "From 1965-2012 - Outliers: (California: 2249, Texas: 627, Florida: 1069)",
    color = "MLB Percent"
  )
```

@@

# To create redraft_gap, I took the full data of unsigned high school players
# and their subsequent draft selections. I grouped the data by player_id, and
# filtered for only the initial pick and the pick which they eventually signed.
# I also filtered for only players who ultimately made the Major Leagues. I made
# sure there were only two rows per player and subtracted the difference in
# years from their initial draft to when they signed. I filtered out a handful
# of observations in which different players shared an ID and were drafted many
# years apart. I then sliced one observation from each player and found the mean
# of the new signing_gap column.

>>>>

```{r prep_war, include=FALSE}

@@

```{r master, include=FALSE}

@@

```{r master_edit, include=FALSE}

@@

```{r add_MLB_years, include=FALSE}

@@

```{r add_pos, include=FALSE}

@@

```{r by_round, echo=FALSE}
draft_2000_2012 <- draft %>%
  filter(year >= 1990 & year <= 2011)

@@

```{r grow_talent, echo=FALSE}
grow_talent <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(decade = ifelse(year %in% 1970:1979, 1970,
                                 ifelse(year %in% 1980:1989, 1980,
                                        ifelse(year %in% 1990:1999, 1990,
                                               ifelse(year %in% 2000:2009, 2000,
                                                      ifelse(year %in% 2010:2019, 2010, NA)))))) %>%
  filter(year >= 1980 & year <= 2009) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(teamname) %>%
  summarize(mlb = sum(mlb_made), 
            total = sum(ignore),
            percent_mlb = sum(mlb_made) / sum(ignore))

@@

```{r hs_by_round, echo=FALSE}

@@

```{r college_by_round, echo=FALSE}
college_signed <- master %>%
  filter(source == "C" & signed == "Y") %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))

@@

```{r hs_unsigned, include=FALSE}

@@

```{r redraft_function, include=FALSE}

@@

```{r redraft_table, include=FALSE}

@@

```{r redraft_prob, echo=FALSE}

@@

```{r round_change, echo=FALSE}
redraft_table %>%
  ggplot(aes(round, mean_round_diff)) +
  geom_point(na.rm = TRUE) +
  geom_line(aes(group = start_year, color = start_year), na.rm = TRUE) +
  labs(
    x = "Round Range Drafted out of High School",
    y = "Average Improvement Re-draft Round",
    color = "Time Frame",
    title = "Average Change in Round of Re-drafted Unsigned High School Picks",
    subtitle = "Organized by initial round range and time period"
  ) +
  theme_light() +
  scale_color_viridis_c() +
  scale_x_continuous(breaks = c(5, 10, 20, 30, 40, 50)) +
  scale_y_continuous(breaks = c(-10, -5, 0, 10, 20)) +
  geom_hline(color = "red", linetype = "dashed", yintercept = 0)
```

@@

```{r career_peak, echo=FALSE}

@@

```{r debut_age, echo=FALSE}

@@

```{r career_length, echo=FALSE}

@@

```{r career_war, echo=FALSE}

@@

```{r US_map, echo=FALSE}

@@

```{r state_summary, echo=FALSE}
state_mlb %>%
  filter(big_state == 0) %>%
  ggplot(aes(full, drafted, color = percent_mlb)) +
  coord_flip() +
  geom_point() +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300, 350)) +
  theme_gray() +
  theme(axis.text.y = element_text(size = 7.5)) +
  scale_color_viridis_c() +
  labs(
    x = "State",
    y = "Number of Players Drafted",
    title = "Number of High School Players Drafted by State",
    subtitle = "From 1965-2012 - Outliers: (California: 2249, Texas: 627, Florida: 1069)",
    color = "MLB Percent"
  )
```

@@

```{r signing_gap, echo=FALSE}

# To create redraft_gap, I took the full data of unsigned high school players
# and their subsequent draft selections. I grouped the data by player_id, and
# filtered for only the initial pick and the pick which they eventually signed.
# I also filtered for only players who ultimately made the Major Leagues. I made
# sure there were only two rows per player and subtracted the difference in
# years from their initial draft to when they signed. I filtered out a handful
# of observations in which different players shared an ID and were drafted many
# years apart. I then sliced one observation from each player and found the mean
# of the new signing_gap column. Slicing won't affect the calculation but makes
# the data easier to look at.
